\documentclass[review]{elsarticle}

\makeatletter
\def\@author#1{\g@addto@macro\elsauthors{\normalsize%
    \def\baselinestretch{1}%
    \upshape\authorsep#1\unskip\textsuperscript{%
      \ifx\@fnmark\@empty\else\unskip\sep\@fnmark\let\sep=,\fi
      \ifx\@corref\@empty\else\unskip\sep\@corref\let\sep=,\fi
      }%
    \def\authorsep{\unskip,\space}%
    \global\let\@fnmark\@empty
    \global\let\@corref\@empty  %% Added
    \global\let\sep\@empty}%
    \@eadauthor={#1}
}
\makeatother

\usepackage{lineno}
\usepackage{color}
\usepackage[hidelinks]{hyperref}



\modulolinenumbers[5]

\journal{Journal of \LaTeX\ Templates}

%%%%%%%%%%%%%%%%%%%%%%%
%% Elsevier bibliography styles
%%%%%%%%%%%%%%%%%%%%%%%
%% To change the style, put a % in front of the second line of the current style and
%% remove the % from the second line of the style you would like to use.
%%%%%%%%%%%%%%%%%%%%%%%

%% Numbered
%\bibliographystyle{model1-num-names}

%% Numbered without titles
%\bibliographystyle{model1a-num-names}

%% Harvard
%\bibliographystyle{model2-names.bst}\biboptions{authoryear}

%% Vancouver numbered
%\usepackage{numcompress}\bibliographystyle{model3-num-names}

%% Vancouver name/year
%\usepackage{numcompress}\bibliographystyle{model4-names}\biboptions{authoryear}

%% APA style
%\bibliographystyle{model5-names}\biboptions{authoryear}

%% AMA style
%\usepackage{numcompress}\bibliographystyle{model6-num-names}

%% `Elsevier LaTeX' style
\bibliographystyle{elsarticle-num}
%%%%%%%%%%%%%%%%%%%%%%%

\begin{document}

\begin{frontmatter}

\title{Barreling formation during the axial compressive experiments on cubic
samples with orthotropic properties {\color{red} Preliminary title}}
%%\tnotetext[mytitlenote]{Fully documented templates are available in the
% elsarticle package on \href{http://www.ctan.org/tex-archive/macros/latex/contrib/elsarticle}{CTAN}.}

%% Group authors per affiliation:






%%\fntext[fn1]{This is the specimen author footnote.}
%%\fntext[fn2]{Another author footnote, but a little more longer.}
%%\fntext[fn3]{Yet another author footnote. Indeed, you can have any number of
% author footnotes.}

\author{Alexey Vorobyev\corref{cor1}}
\ead{alexey.vorobyev@angstrom.uu.se}

\cortext[cor1]{Corresponding author}

\author{Nico P. van Dijk}
\author{Kristofer Gamstedt}

\address{Uppsala University, Division of Appplied Mechanics,
Uppsala, Sweden }



\begin{abstract}
This template helps you to create a properly formatted \LaTeX\ manuscript.
\end{abstract}

\begin{keyword}
\texttt{elsarticle.cls}\sep \LaTeX\sep Elsevier \sep template
\MSC[2010] 00-01\sep  99-00
\end{keyword}

\end{frontmatter}

\linenumbers

\section{Introduction}
\begin{itemize}
\color{red}  
\item what problem was studied
\item Introduction of the problem
\item Give the context of the problem
\item Reviews of previous works
\item Justification of work
\item Scopes and objectives
\item Interest the reader
\item Provide the transition to the rest
\end{itemize}

\section{Materialss and Methods}
\section{Model}

The finite element program COMSOL Multiphysics 4.4 \cite{Comsol} was used for
the experimental simulations.
The entire cube with singular side was modeled with 3D solid elements.
The platens of universal testing mashine were not considered in the model.
Instead compressive load was directly applied perpendicularilly to the top
surface of the cube. 
The bottom surface of the cube was constrained from the displacement along
Z axis. However its two mutually orthogonal edges were alloud to move in
perpendicular directions along X and Y axises. The same was done for the edges in the top surface.

\begin{description}
\item[{\color {red}Friction}]
\end{description}

In order to simulate the friction between the platens and the sample we have
introduced friction parameters that were applied to the mutually orthogonal
edges on the top and the bottom surface of the cube. Those parameters were
variating from zero and up to the value which equals to the stiffness along
Z axis of the cube.


{\color {red}Add the picture that is showing the axises and add the
description to the the text in accodance to that. Add the bottom surface, the
free edges the friction, the coeffitients, the variability of frictions that }
\begin{itemize}
\color{red}

\item How was the rproblem studied 
\item Description of FEM model, parameters, application, details of the model
\item Describe the experimental setup, materials and procedure
\end{itemize}


\section{Results and Discussions}
\begin{itemize}
\color{red}
\item What were the findings?
\item Use diagrams and/or tables, objective and truthful presentation
\item Results and discussion distinguishable
\item New and old results and discussion
\end{itemize}


\section{Conclusions}

\section*{Acknowledgements}

\section*{References}

\bibliography{mybibfile}

\end{document}